Wetting properties of the adhesive fluid allows beetles to attach to surfaces not just in air but also underwater

### 2021-02-15 source/tex/ladybug_adhesion.tex
Latex edits made by Thomas

\title{Wetting of adhesive fluid controls insect adhesion in air and underwater}

@@

\begin{document}
\begin{abstract}
Insects like beetles can stick to various surfaces using hairy pads
on their legs. It was previously shown that these pads can even attach
underwater, presumably due to an air bubble trapped around the pad.
However, the bubble's contribution to adhesion via capillary force
remained unclear. To investigate the role of the bubble, we measured\emph{
in-vivo} underwater adhesion of a ladybug's pad, in the presence and
absence of the trapped bubble and compare it with its adhesion in
air. Our experiments reveal that on a hydrophobic substrate, even
without a bubble, the pad can show adhesion underwater comparable
to that in air. On a hydrophilic substrate, underwater adhesion is
significantly reduced, with or without a trapped bubble. To explain
these results, we develop a simple theoretical model for the net adhesion
of a hairy pad due to capillary forces. Our results demonstrate that
the wetting properties of the adhesive fluid determines the insect's
adhesion in both air and underwater conditions.
\end{abstract}

@@

The question of how insects and other small animals can walk on smooth
surfaces against gravity has fascinated scientists for at least the
past three centuries \cite{RN198,RN59}. We now know that such animals
are able to adhere by using specialized organs on their feet called
adhesive pads. These adhesive pads exist in a variety of types depending
on the animal, but are generally categorized into: 1) ``smooth pads''
found in ants\cite{RN201}, stick insects \cite{RN182}, etc. and
2) ``hairy pads'' seen in flies \cite{RN155}, geckos \cite{RN202}
and others. The hairy pads show: 1) compliance to rough surfaces due
to their lower effective modulus, 2) angle dependent adhesion due
to asymmetric hair geometry and 3) self-cleaning capability \cite{RN20},
which makes them suitable to adhere to most surfaces reversibly. Many
of these insects pads also secrete an adhesive fluid, as seen in flies
and ants \cite{RN201} (``wet adhesion''), while others such as
spiders and geckos rely on their dry hairy pads for attachment (``dry
adhesion''). In the ``wet adhesion'' case, fluid secretion can
enforce adhesion through surface tension and viscous forces \cite{RN71},
while, ``dry adhesion'' relies mostly on van der Waals forces \cite{RN202}.

Terrestrial beetles such as the dock beetle or the ladybug have hairy
pads consisting of a dense array of hair-like structures called setae.
The setae tips can be discoidal, spatula or pointed shaped, which
are distributed throughout the pad depending on sex or species\cite{RN19}.
Single seta force measurements revealed that discoidal shaped seta
shows larger pull-off force than spatula and pointed setae\cite{RN79},
illustrating the role of hair geometry in adhesion. The tip of each
seta secretes approximately one femtoliter of oily adhesive fluid
\cite{RN108}. The fluid's chemical composition is identified as a
mixture of mostly long chain hydrocarbons\cite{RN96} with traces
of triglycerides, fatty acids and cholesterol\cite{RN221,RN222}.
A recent study by Gernay et. al.\cite{RN77}, based on an elastocapillary
model, has been able to reasonably predict single seta adhesion forces
theoretically, confirming the dominant role of surface tension in
the ``wet adhesion'' of beetles.

While most of the studies on insect adhesion are done under natural
conditions in air, insect attachment underwater has been relatively
unexplored. Typically, underwater adhesion is complicated to achieve
due to the difficulty in displacing the water layer and enable good
contact\cite{RN123}. Regardless, a study on leaf beetles\cite{RN87}
has revealed that they can in fact attach quite well to surfaces underwater.
Its hairy pad traps an air bubble underwater, which dewets the surface
on contact. It has been hypothesized that a combination of capillary
forces due the air bubble and hair secretions within the dewetted
area results in its adhesion underwater. However, a detailed investigation
of the bubble's contribution and necessity to adhere to different
surfaces is lacking. Geckos are also known to adhere underwater, where
its shear adhesion force on hydrophobic substrates are similar in
both air and underwater conditions. Interestingly, its adhesion on
a fluorinated substrate is even larger underwater than in air\cite{RN15}.
This has been partially explained by a thermodynamic work of adhesion
model, assuming full displacement of water at the interface, leading
to a dry ``van der Waals'' contact of hairs with the surface\cite{RN199}.

The goal of this paper is to provide a generalized picture of adhesion
for insects which use hairy pads and secrete a oily fluid for attachment.
First, we measured adhesion of a single constrained pad of a live
ladybug beetle in air and underwater conditions, both on smooth hydrophilic
and hydrophobic glass surfaces, with a microscopic observation of
the contact process. Second, we developed a simple theoretical model
considering capillary forces to predict the net adhesion force of
a hairy pad under different conditions. The case of underwater adhesion
was studied both in the presence and absence of a trapped bubble,
to decouple the bubble's role in the insect's adhesion. Finally, we
discuss key insights gained from our experiments and model with regards
to understanding adhesion in other animals.

@@

Normal adhesion force measurements on a restrained leg of a live ladybug
beetle were performed. We characterize adhesion by the pull-off force
during detachment. Measurements were done against smooth glass and
fluorinated surfaces to represent hydrophilic and hydrophobic substrates
respectively. When no water was present, we labeled the contact type
as ``\emph{in air}''. For the underwater conditions, measurements
were done both in the presence and absence of a trapped bubble (``\emph{underwater:
bubble}'' and ``\emph{underwater: no bubble}'', respectively) to
investigate the bubble's role in underwater adhesion. Adhesion force
for each of the labeled contact types were compared for both substrates.

@@

Seven-spotted male adult ladybug beetles (\emph{Coccinella septempuctata})
purchased from Katz Biotech (Baruth, Germany) were used for adhesion
tests. The beetles were housed in a plastic box filled with leaves,
twigs and stones at room temperature and 60-80\% relative humidity
with daily access to sunlight. They were fed with raisins, honey and
water\emph{ ad libitum}.

Each leg of the beetle has a pair of hairy pads covered with mostly
discoidal shaped setae, capable of strong adhesion. For the test,
we only allowed the distal-end pad to make contact. The beetle's leg
was constrained similar to the method described by Bullock et al \cite{RN19}.
A steel ball fixed with a piece of thick solder wire served as a rotatable
holder to fix the beetle and align its leg (Figure \ref{fig:Setup}).
The beetle was first anesthetized using CO\textsubscript{2} sublimating
from a piece of dry ice and then glued to the steel ball on its back.
Its front left leg was carefully fixed to the solder wire of the holder
using Blue-Tac. Its claws were fixed using epoxy glue to prevent any
wiggling. A small piece of non-sticky Teflon tape helped to keep its
other legs tucked close to the body and avoid their interference during
the adhesion test.

After measurements, the beetle was freed by carefully removing the
epoxy glue and Blue-Tac without harming it and set free.

The substrate wettability was characterized by dynamic contact angle
measurements, performed with a DataPhysics OCA 35 contact angle goniometer.
Milli-Q water and n-hexadecane were used as test liquids. Advancing
and receding contact angles were measured for a maximum drop volume
of 10 \textgreek{m}l and with 0.5 \textgreek{m}l/s flow rate.

@@

Adhesion measurements were performed on a custom force measurement
setup developed in-house (Figure \ref{fig:Setup}). A fiber optic
displacement sensor (\emph{Philtec D20, PHILTEC, Inc. USA}) together
with a steel bending beam (spring constant = 68.1 N/m) constitutes
the vertical force sensor. Beam deflection was calibrated using 4
different known weights to get the corresponding force. A plastic
3D printed substrate holder was glued to the end of the bending beam.
The holder was designed to enable switching from one substrate to
another without removing any glue. It also had transparent side walls
which allowed us to fill it with water for the underwater experiments
as well as observe the contact. The sensor was mounted on a stage
consisting of a X-piezo, used for precise lateral movements, XYZ motors,
for coarse movements and a goniometer, for adjusting substrate alignment
with the optics. Additionally, a separate Z-piezo, fixed upright,
was used for vertical up-down motion, bringing the insect in contact
with the substrate from the top. A 3 axis manual micro-manipulator
together with the rotatable steel ball allowed good alignment of the
beetle's foot to the substrate. A coaxial illuminated tube microscope
(\emph{Navitar}) with 2$\times$ objective and a stereo-microscope
with 1$\times$ objective (\emph{Wild Heerbrugg}) fit with cameras
were used to record the sample contact with the substrate from ventral
and side views respectively. Pad contact area was visualized through
the substrate in total reflection mode by the ventral view camera.
The data acquisition from the force sensor and cameras, together with
the appropriate piezo motion steps were synchronized using a custom
LABVIEW program. Force data was acquired at a sample rate of 984 Hz,
averaged to 512 points per motion step. Videos were recorded at 20
frames per second.

The vertical and lateral piezos were together used to perform approach-retract
adhesion tests with the substrate to get the pull-off force. However,
instead of a simple down-up motion, some additional motion steps were
included (Figure \ref{fig:Setup}). A 100 \textgreek{m}m lateral sliding
motion was done after the leg makes contact, to give it a proximal
pull which will orient its hairs with the substrate \cite{RN19}.
An additional 10 \textgreek{m}m compression step (approach) was done
to ensure all hairs were loaded in compression and made good contact
with the surface. A short pause (1 s) was introduced to minimize any
viscoelastic effects before finally retracting the leg away from the
substrate. All approach, retract and lateral slide motion was done
at a speed of 62.5 \textgreek{m}m/s. Ventral view video recordings
were used for contact area extraction while the side view imaging
was used to visually aid orienting the pad with the substrate before
a test.

For underwater experiments, 1 ml Milli-Q water was pipetted into the
substrate holder. In order to achieve an underwater contact without
a trapped air bubble, the water was first degassed in a vacuum chamber
at 10 mbar pressure for 3 hours and used immediately. Before experiment,
the pad was repeatedly brought into contact with the surface 10 times
to equilibriate the pad system. 5 force measurements were subsequently
performed on a fresh spot of the substrate and averaged for data analysis.
Experiments were repeated with 5 individual beetles for each type
of contact and substrate. In total, 30 beetles were tested.

\begin{figure}[H]
\begin{centering}
\includegraphics[scale=0.5]{Figure1-Setup_schematic}
\par\end{centering}
\caption{\label{fig:Setup} Adhesion test setup. The recorded force data and
contact area of distal pad are shown in the plot, in which, the shaded
regions represent distinct piezo motion steps, negative force values
represent attraction and the minimum force peak during the final retraction
step is the adhesion force.}
\end{figure}

A previous study on archanids \cite{RN223} reported that its secreted
fluid does not dissolve in water. To confirm if even the beetle retains
its adhesive fluid underwater, we perform Field Desorption Mass Spectroscopy
(FDMS) using a ZAB 2-SE-FPD spectrometer (VG Instruments). The measurements
were done on the extracted secretions before and after rinsing its
legs with water. The middle leg of an Asian ladybird (\emph{Harmonia
axyridis}) was immersed in 50 \textmu L THF for 20 min and then transferred
to the measurement chamber of the FDMS. As a reference, pure THF was
used. The second middle leg of the same ladybird was subsequently
immersed in 100 \textmu L Milli-Q water for 15 min, then in THF for
20 min and then transferred to the measurement chamber of the spectrometer.
Molecular composition was extracted from the peak positions of the
FDMS spectra.

@@

@@

In air, adhesion forces of the distal pad of ladybug beetle against
glass and PFOTS are rather similar; no significant differences are
detected (Figure \ref{fig:Effect-of-contact} and Table \ref{tab:Statistical-analysis}).
In contrast, underwater adhesion on PFOTS surface is significantly
larger than on glass (p < 0.001). This stronger adhesion on PFOTS
is observed both in the presence and absence of a trapped bubble.
In both cases, adhesion force reach similar values as in air. In contrast,
on glass, adhesion underwater is significantly reduced as compared
to dry conditions, irrespective of the presence of a trapped bubble
(p $\leq$ 0.002). Underwater adhesion on glass tends to be slightly
higher in the presence of a bubble (CLES = 0.84). However, this difference
is small and not statistically significant (p = 0.07).

@@

\begin{figure}[H]
\includegraphics[width=0.7\linewidth]{Figure3-Model_schematic}\caption{\label{fig:Model}The capillary bridge model. The hairs make contact
with the substrate in three ways: a) \emph{In air}, where the adhesive
fluid bridges are surrounded by air; b) \emph{Underwater: no bubble},
where the adhesive fluid bridges are fully surrounded by water; c)\emph{
Underwater: bubble}, where part of the adhesive fluid bridges are
inside the bubble while others are outside in water. The corresponding
ventral view contact images of the beetle's pad are shown on the right.}
\end{figure}
We model the hairy pad as an array of $N$ cylindrical rods of length,
$L$, and diameter, $D_{h}$, fixed to a flat circular pad of diameter,
$D_{p}$ (Figure \ref{fig:Model}). The hairs and the pad are assumed
to be perfectly rigid, for simplicity. The tip of each hair has an
adhesive fluid of volume, $V_{f}$, making contact with the substrate.
The fluid is pinned to the circumference of the hair and forms a capillary
bridge of height, $d$. Similar to our experiments, we consider three
types of contacts for the pad: 1) \emph{In air}, 2) \emph{Underwater:
no bubble} and 3) \emph{Underwater: bubble}. In the third case, a
bubble of volume, $V_{b}$, is trapped between the hairs and pinned
to the pad circumference.

To characterize the adhesive fluid and bubble volume we define two
radii, $s_{f}$ and $s_{b}$, respectively, by $V_{f}=\frac{4}{3}\pi s_{f}^{3}$
and $V_{b}=\frac{4}{3}\pi s_{b}^{3}$. Here, $s_{f}$ and $s_{b}$
are the radii of spheres with equivalent volumes. Fluid and bubble
radii are assumed to scale proportional to their corresponding pinned
contact diameter. We thus defined the size parameters, $\phi_{f}=D_{h}/\left(2s_{f}\right)$
and $\phi_{b}=D_{p}/\left(2s_{b}\right)$ for the fluid and bubble
respectively, to conveniently scale their volumes relative to the
hair and pad diameters they were pinned to.

@@

All lengths are normalized w.r.t. $s_{f}$ and forces are normalized
w.r.t. $\gamma_{fa}s_{f}$. Interfacial tension values are fixed relative
to $\gamma_{fa}$. Non dimensional bubble volume is expressed as,
$\hat{V}_{b}=V_{b}/s_{f}^{3}$

@@

First, we calculate force-distance curves for a single pinned liquid
capillary bridge. Second, the effect of substrate on the force-distance
curves of the hairy pad system is compared for each type of contact.
Third, the effect of varying hair diameter, $D_{h}$, on net adhesion
is studied. Finally, we look at the effect of changing the bubble
volume, $\hat{V}_{b}$, on the net underwater adhesion.

@@

Forces due to a single pinned capillary liquid bridge in contact with
a substrate are obtained via Surface Evolver simulations (Figure \ref{fig:Single-bridge}).
We see that, generally, the shape of the liquid meniscus determines
the strength of its adhesion force. High adhesion is seen for contact
angles less than $\sim$ 70\textdegree{} due to a net negative curvature
of the meniscus, while low adhesion is seen for contact angles greater
than $\sim$ 150\textdegree{} due to its net curvature being close
to zero. The Laplace pressure contribution to the net adhesion force
dominates for contact angles less than 100\textdegree{} (Figure \ref{fig:Single-bridge}b).
Interestingly, its contribution to the adhesion force is mostly non-repulsive
for contact angles greater than 90\textdegree . This is because, the
low volume of the liquid and its pinned contact line prevents the
meniscus from having a high positive curvature due to geometric constraints.
Only for a contact angle of 150\textdegree , the liquid's curvature
becomes positive, manifested in its slightly repulsive Laplace contribution.
Surface tension makes a significant contribution to the net force
only for a small range of contact angles close to 90\textdegree .
For contact angles greater than 150\textdegree , the net adhesion
force approaches zero.

@@

\subcaption{Force contributions}%
\end{minipage}\caption{\label{fig:Single-bridge}Normalized capillary force of a single liquid
bridge in contact with a substrate and pinned to a circular perimeter
on top. Fluid size parameter, $\phi_{f}=2$. Negative force values
represents attraction. a) Force-distance curves are shown for different
contact angles of the liquid with the substrate. b) Adhesion forces,
calculated from the minima of the corresponding force-distance curves,
are plotted as a function of contact angle with the substrate, together
with its Laplace and surface tension components (equation \ref{eq:f_bridge}).
Simulation snapshots of the liquid meniscus corresponding to angles
6\textdegree{} and 150\textdegree{} are depicted.}
\end{figure}

@@

The normalized force-distance curves of a hairy pad system on a hydrophilic
and hydrophobic substrate are predicted based on the capillary bridge
model and compared for the different contact types (Figure \ref{fig:Effect-of-substrate}).
The forces in each case are calculated from equations (\ref{eq:f_air/water})
and (\ref{eq:f_bubble}) for fixed geometric and interfacial properties
(Table \ref{tab:Model-parameters}).

@@

\begin{figure}[H]
\centering{}\includegraphics{Figure5-Model_effect_of_substrate}\caption{\label{fig:Effect-of-substrate}Theoretical force-distance curves
of a hairy pad system on a hydrophilic and hydrophobic substrate in
air and underwater conditions. A negative force value represents attraction.
Normalized forces are calculated from the capillary bridge model,
with model parameters listed in Table \ref{tab:Model-parameters}.
The bubble's contribution to the net force for an \emph{underwater:
bubble} contact is denoted by plus symbols. Insets represent the \emph{underwater:
bubble }contact for each substrate.}
\end{figure}

>>>>

\title{Wetting properties of the adhesive fluid allows beetles to attach to surfaces not just in air but also underwater}

@@

\begin{document}
\begin{abstract}

Many beetles can climb smooth surfaces using hairy adhesive pads on their legs. It was previously shown that a terrestrial beetle can even adhere and walk underwater. The naturally hydrophobic hairs trap an air bubble around the pads, allowing the hairs to make contact to the substrate like in air. However, it remained unclear to what extend such an air bubble is necessary for underwater adhesion and if the bubble contributes to the net adhesive force. To investigate the role of the bubble, we measured the adhesive forces in individual legs of live but constrained ladybug beetles underwater in the presence and absence of a trapped bubble and compared it with its adhesion in air. Our experiments revealed that on a hydrophobic substrate, even without a bubble, the pads show adhesion comparable to that in air. On a hydrophilic substrate, underwater adhesion is significantly reduced, with or without a trapped bubble. We modelled the adhesion of a hairy pad using capillary forces. Coherent with our experiments, the model demonstrates that the wetting properties of the adhesive fluid alone can determine the insects' adhesion in both air and underwater conditions and that an air bubble is not a prerequisite for their underwater adhesion. 
\end{abstract}

@@

The question on how insects and other small arboreal animals climb smooth and slippery
surfaces has fascinated scientists for the past three centuries \cite{RN198,RN59}. We now know that such animals are able to adhere by using specialised organs on their feet called adhesive pads. These adhesive pads can generally be described as either ``smooth'' or ``hairy''. Several insect orders including earwigs, flies, and beetles \cite{Gorb:2001b} but also several spiders \cite{Coddington:1991} and arboreal lizards \cite{Williams:1982} bear hairy pads. Hairy pads show 1) compliance to rough surfaces due to their lower effective modulus, 2) angle dependent adhesion due to asymmetric hair geometry and 3) self-cleaning capability \cite{RN20}, which makes them suitable to adhere to most surfaces reversibly. The hairs themselves (setae) can branch into smaller fibrillar units (spatulae) like seen in spiders and lizards but are typically undivided in most insects. The hairs in many insects can however exhibit different tip geometries, including discoidal, spatula shaped or pointed tips, and distributed throughout the pad depending on sex or species\cite{RN19}. Single seta force measurements revealed that discoidal shaped seta show larger pull-off forces than spatula shaped or pointed setae\cite{RN79}, illustrating the role of hair geometry in adhesion. All insect pads secrete an adhesive fluid while spiders and geckos rely on their dry hairy pads for attachment (``dry adhesion''). In the ``wet adhesion'' case, fluid secretion can enforce adhesion through surface tension and viscous forces \cite{RN71}, while, ``dry adhesion'' relies mostly on van der Waals forces \cite{RN202}.

While most of the studies on insect adhesion focused on terrestrial species, underwater insect attachment is much more rare and has been relatively unexplored. Some aquatic insects like diving beetles \cite{Chen:2014} or midge larva \cite{Kang:2020} using suction cups to adhere to surfaces. However, underwater adhesion using secreted liquids (glue-like substances or the adhesive fluid) requires the displacement of the water in the interface first and a spreading of the fluid on the substrate. Furthermore, the spreading coefficient of the secreted liquid needs to be larger than that of the water in order to utilise the interfacial tension between the liquids as an adhesive force. One relative simple approach is to use an air bubble around the adhesive organs similar to the air bubbles many secondary aquatic insects and spiders carry on their body for breathing underwater \cite{Seymour:2013}. This has been shown in a recent study by \citet{RN87} on the ability of a terrestrial leaf beetle which can attach quite well to surfaces underwater by using such an air bubble. Their naturally hydrophobic hairs trap the bubble around the pads when being submerged, which de-wets the surface effectively on contact. It has been hypothesised that a combination of capillary forces due the air bubble and hair secretions within the dewetted area results in its adhesion underwater. However, it remained unclear whether an air bubble is strictly necessary and its exact contribution to the adhesive force. The oily adhesive fluid found in insects alone might be sufficient in creating the necessary interfacial tension even without an bubble, given that the adhesive fluid remains on the hairs when submerged. In beetles, the tip of each seta secretes approximately one femtoliter of oily adhesive fluid \cite{RN108}. The fluid's chemical composition is identified as a mixture of mostly long chain hydrocarbons\cite{RN96} with traces
of triglycerides, fatty acids and cholesterol\cite{RN221,RN222} rendering it immiscible with water. %A recent study by Gernay et. al.\cite{RN77}, based on an elastocapillary model, has been able to reasonably predict single seta adhesion forces theoretically, confirming the dominant role of surface tension in the ``wet adhesion'' of beetles.

% Geckos are also known to adhere underwater, where its shear adhesion force on hydrophobic substrates are similar in both air and underwater conditions. Interestingly, its adhesion on a fluorinated substrate is even larger underwater than in air\cite{RN15}. This has been partially explained by a thermodynamic work of adhesion model, assuming full displacement of water at the interface, leading to a dry ``van der Waals'' contact of hairs with the surface\cite{RN199}.

The goal of this paper is to provide a generalised picture of adhesion in insects which use hairy pads and secrete a oily fluid for attachment. We used the ladybug beetle (\emph{Coccinella septempunctata}) as an animal model to first experimentally measure adhesion of individual adhesive pads in air and underwater conditions, both on smooth hydrophilic and hydrophobic glass surfaces. We further tested whether the chemical profile of the adhesive fluid changes when the hairs being submerged in water. Second, we developed a simple theoretical model considering capillary forces to predict the net adhesion force of a hairy pad under different conditions. The case of underwater adhesion was studied both in the presence and absence of a trapped bubble, to decouple the bubble's role in the insect's adhesion. Finally, we
discuss key insights gained from our experiments and model with regards to understanding adhesion in other animals.

@@

Normal adhesion force measurements on a restrained leg in a live
beetle were performed. We characterised adhesion by the pull-off force
during detachment and tested smooth glass and
fluorinated surfaces representing hydrophilic and hydrophobic substrates
respectively. When no water was present, we labelled the contact type
as ``\emph{in air}''. Underwater, measurements
were done both in the presence and absence of a trapped bubble (``\emph{underwater:
bubble}'' and ``\emph{underwater: no bubble}'', respectively) to
investigate the bubble's role in underwater adhesion. Adhesion force
for each of the labelled contact types were compared for both substrates.

@@

Seven-spotted male adult ladybug beetles (\emph{Coccinella septempuctata})
purchased from Katz Biotech (Baruth, Germany) and housed in a plastic box filled with leaves,
twigs and stones at room temperature and 60-80\% relative humidity
with daily access to sunlight. They were fed with raisins, honey and
water \emph{ad libitum}.

 %The beetle's leg was constrained similar to the method described by Bullock et al \cite{RN19}.
An individual beetle was first carefully anesthetised using small amounts of CO\textsubscript{2} sublimating
from a piece of dry ice and then glued with a small dollop of epoxy glue on its elytra to the underside of a heavy steel ball. The ball was held in a bracket which allowed free rotational movement of the ball in each direction, thus helping to align the suspended beetle over the substrate (see Fig.~\ref{fig:Setup}). The bracket with the ball and the beetle could be further positioned by manual micromanipulators in all three axes before the experiments. One front left leg was carefully fixed to a piece of soft solder wire coming off the steel ball using Blue-Tac (X) allowing us to further align the leg to the substrate. The claws on the leg were also fixed to the wire using epoxy glue to prevent any further wiggling and to prevent the claws from touching the substrate. Each leg of a male ladybug beetle has two pads. For the test, we only allowed the distal pad to come into contact with the substrate thus minimising partial or bad contact of the other one. A small piece of non-sticky Teflon tape helped to keep other legs tucked close to the body and avoided any interference during the adhesion test. After the measurements, the beetle was freed by carefully removing the epoxy glue and Blue-Tac without harming it and set free.

@@

Adhesion measurements were performed on a custom force measurement
setup developed in-house (Figure \ref{fig:Setup}). A fiber optic
displacement sensor (\emph{Philtec D20, PHILTEC, Inc. USA}) together
with a steel bending beam (spring constant = 68.1 N/m) constitutes
the (vertical) force sensor. Beam deflection was calibrated using 4
different known weights to get the corresponding force. A plastic
3D printed substrate holder was glued to the end of the bending beam.
The holder was designed to enable switching from one substrate to
another without removing any glue. It also had transparent side walls
which allowed us to fill it with water for the underwater experiments
as well as observe the contact. The sensor was mounted on a stage
consisting of a X-piezo, used for precise lateral movements, XYZ motors,
for coarse movements and a goniometer, for adjusting substrate alignment
with the optics. Additionally, a separate Z-piezo, fixed upright,
was used for vertical up-down motion, bringing the insect in contact
with the substrate from the top. A coaxial illuminated tube microscope
(\emph{Navitar}) with 2$\times$ objective and a stereo-microscope
with 1$\times$ objective (\emph{Wild Heerbrugg}) fit with digital video cameras (\emph{FLIR Blackfly S}, 2448 x 2048 pixel; XBasler)
were used to record the sample contact with the substrate from ventral
and side views respectively. Pad contact area was visualised through
the substrate with help of epi-illumination.
The data acquisition from the force sensor and cameras, together with
the appropriate piezo motion steps were synchronised using a custom
LABVIEW program. Force data was acquired at a sample rate of 984 Hz,
averaged to 512 points per motion step. Videos were recorded at 20
frames per second.

The vertical and lateral piezos were used together to perform approach-retract
adhesion tests with the substrate to get the pull-off force. However,
instead of a simple down-up motion, an additional 100 \textgreek{m}m lateral sliding motion was introduced after the leg made contact, to ensure most of the hair tips align well with the substrate \cite{RN19}.
A further 10 \textgreek{m}m compression step (approach) set all hairs in slight compression which helped further contact
with the surface. Next, a short pause (1 s) removed any
viscoelastic effects before finally retracting the leg away from the
substrate. All approach, retract and lateral slide motion was done
at a speed of 62.5 \textgreek{m}m/s. Ventral view video recordings
were used for contact area extraction while the side view imaging
was used to visually aid orienting the pad with the substrate before
a test.

For underwater experiments, 1 ml Milli-Q water was pipetted into the
substrate holder. In order to achieve an underwater contact without
a trapped air bubble, the water was first degassed in a vacuum chamber
at 10 mbar pressure for 3 hours and used immediately. Before the experiments,
the pad was brought into contact with the surface 10 times repeatedly 
to equilibrate the pad system (X what do you mean by equilibrate?).

Five force measurements were subsequently performed on a fresh spot of the substrate and averaged for data analysis. Experiments were repeated with five individual beetles for each type of contact and substrate. In total, 30 beetles were tested.

\begin{figure}[H]
\begin{centering}
\includegraphics[scale=0.5]{Figure1-Setup_schematic}
\par\end{centering}
\caption{\label{fig:Setup} Adhesion setup (for explanation see text). The recorded force data and
contact area of a distal pad are shown in the plot, in which, the shaded
regions represent distinct movements like approach, lateral pull, pre-load and detachment... (please explain which ones X). Negative force values
represent attraction and the minimum force peak during the final retraction
step is the adhesion force used for further analysis. An animated version of a typical force recording is available in the Supplementary Material Xshould we provide one?}
\end{figure}

@@

The substrate wettability was characterised by dynamic contact angle
measurements, performed with a DataPhysics OCA 35 contact angle goniometer.
Milli-Q water and n-hexadecane were used as test liquids. Advancing
and receding contact angles were measured for a maximum drop volume
of 10 \textgreek{m}l and with 0.5 \textgreek{m}l/s flow rate.

A previous study on archanids \cite{RN223} reported that its secreted
fluid does not dissolve in water. To test whether the beetles retain
their adhesive fluid underwater unchanged, we performed a Field Desorption Mass Spectroscopy
(FDMS) using a ZAB 2-SE-FPD spectrometer (VG Instruments). The measurements
were done on the extracted secretions before and after rinsing its
legs with water. The middle leg of an Asian ladybird (\emph{Harmonia
axyridis} X the fact we are introducing a new species is a bit odd and could raise a question with the reviewer but I don't know a good way around it. we could bring it in the introduction and say that these are preliminary/unpublished results. that would be perfectly viable) was immersed in 50 \textmu L THF for 20 min and then transferred
to the measurement chamber of the FDMS. As a reference, pure THF was
used. The second middle leg of the same ladybird was subsequently
immersed in 100 \textmu L Milli-Q water for 15 min, then in THF for
20 min and then transferred to the measurement chamber of the spectrometer.
Molecular composition was extracted from the peak positions of the
FDMS spectra.

@@

In air, adhesion forces of the distal pad of ladybug beetle against
glass and PFOTS were similar, i.e. no significant differences were
detected (Figure \ref{fig:Effect-of-contact} and Table \ref{tab:Statistical-analysis}).
In contrast, the underwater adhesion on a PFOTS surface was significantly
larger than on glass (p < 0.001). This stronger adhesion on PFOTS
is observed both in the presence and absence of a trapped bubble.
In both cases, adhesion force reach similar values as in air. In contrast,
on glass, adhesion underwater is significantly reduced as compared
to dry conditions, irrespective of the presence of a trapped bubble
(p $\leq$ 0.002). In the presence of a bubble, underwater adhesion on glass was slightly higher (CLES = 0.84, p = 0.07).

@@

(X check for the past tense where applicable X)
\begin{figure}[H]
\includegraphics[width=0.7\linewidth]{Figure3-Model_schematic}\caption{\label{fig:Model}The capillary bridge model. The hairs make contact
with the substrate in three ways: a) \emph{In air}, where the adhesive
fluid bridges are surrounded by air; b) \emph{Underwater: no bubble},
where the adhesive fluid bridges are fully surrounded by water; c)\emph{
Underwater: bubble}, where part of the adhesive fluid bridges are
inside the bubble while others are outside in water. The corresponding
ventral view contact images of the beetle's pad are shown on the right.}
\end{figure}

We modelled the hairy pad as an array of $N$ cylindrical rods of length,
$L$, and diameter, $D_{h}$, fixed to a flat circular pad of diameter,
$D_{p}$ (Figure \ref{fig:Model}). The hairs and the pad are assumed
to be perfectly rigid, for simplicity. The tip of each hair has an
adhesive fluid of volume, $V_{f}$, making contact with the substrate.
The fluid is pinned to the circumference of the hair and forms a capillary
bridge of height, $d$. Similar to our experiments, we consider three
types of contacts for the pad: 1) \emph{In air}, 2) \emph{Underwater:
no bubble} and 3) \emph{Underwater: bubble}. In the third case, a
bubble of volume, $V_{b}$, is trapped between the hairs and pinned
to the pad circumference.

To characterise the adhesive fluid and bubble volume we defined two
radii, $s_{f}$ and $s_{b}$, respectively, by $V_{f}=\frac{4}{3}\pi s_{f}^{3}$
and $V_{b}=\frac{4}{3}\pi s_{b}^{3}$. Here, $s_{f}$ and $s_{b}$
are the radii of spheres with equivalent volumes. Fluid and bubble
radii are assumed to scale proportional to their corresponding pinned
contact diameter. We thus defined the size parameters, $\phi_{f}=D_{h}/\left(2s_{f}\right)$
and $\phi_{b}=D_{p}/\left(2s_{b}\right)$ for the fluid and bubble
respectively, to conveniently scale their volumes relative to the
hair and pad diameters they were pinned to.

@@

All lengths are normalised w.r.t. $s_{f}$ and forces are normalized
w.r.t. $\gamma_{fa}s_{f}$. Interfacial tension values are fixed relative
to $\gamma_{fa}$. Non dimensional bubble volume is expressed as,
$\hat{V}_{b}=V_{b}/s_{f}^{3}$

@@

We first calculated force-distance curves for a single pinned liquid
capillary bridge. Second, the effect of substrate on the force-distance
curves of the hairy pad system was compared for each type of contact.
Third, the effect of varying hair diameter, $D_{h}$, on net adhesion
is studied. Finally, we look at the effect of changing the bubble
volume, $\hat{V}_{b}$, on the net underwater adhesion.

@@

Forces due to a single pinned capillary liquid bridge in contact with
a substrate were obtained via Surface Evolver simulations (Figure \ref{fig:Single-bridge}).
We see that, generally, the shape of the liquid meniscus determines
the strength of its adhesion force. High adhesion is seen for contact
angles less than $\sim$ 70\textdegree{} due to a net negative curvature
of the meniscus, while low adhesion is seen for contact angles greater
than $\sim$ 150\textdegree{} due to its net curvature being close
to zero. The Laplace pressure contribution to the net adhesion force
dominates for contact angles less than 100\textdegree{} (Figure \ref{fig:Single-bridge}b).
Interestingly, its contribution to the adhesion force is mostly non-repulsive
for contact angles greater than 90\textdegree . This is because, the
low volume of the liquid and its pinned contact line prevents the
meniscus from having a high positive curvature due to geometric constraints.
Only for a contact angle of 150\textdegree , the liquid's curvature
becomes positive, manifested in its slightly repulsive Laplace contribution.
Surface tension makes a significant contribution to the net force
only for a small range of contact angles close to 90\textdegree .
For contact angles greater than 150\textdegree , the net adhesion
force approaches zero.

@@

\subcaption{Force contributions}%
\end{minipage}\caption{\label{fig:Single-bridge}Normalised capillary force of a single liquid
bridge in contact with a substrate and pinned to a circular perimeter
on top. Fluid size parameter, $\phi_{f}=2$. Negative force values
represents attraction. a) Force-distance curves are shown for different
contact angles of the liquid with the substrate. b) Adhesion forces,
calculated from the minima of the corresponding force-distance curves,
are plotted as a function of contact angle with the substrate, together
with its Laplace and surface tension components (equation \ref{eq:f_bridge}).
Simulation snapshots of the liquid meniscus corresponding to angles
6\textdegree{} and 150\textdegree{} are depicted.}
\end{figure}

@@

The normalised force-distance curves of a hairy pad system on a hydrophilic
and hydrophobic substrate are predicted based on the capillary bridge
model and compared for the different contact types (Figure \ref{fig:Effect-of-substrate}).
The forces in each case are calculated from equations (\ref{eq:f_air/water})
and (\ref{eq:f_bubble}) for fixed geometric and interfacial properties
(Table \ref{tab:Model-parameters}).

@@

\begin{figure}[H]
\centering{}\includegraphics{Figure5-Model_effect_of_substrate}\caption{\label{fig:Effect-of-substrate}Theoretical force-distance curves
of a hairy pad system on a hydrophilic and hydrophobic substrate in
air and underwater conditions. A negative force value represents attraction.
Normalised forces are calculated from the capillary bridge model,
with model parameters listed in Table \ref{tab:Model-parameters}.
The bubble's contribution to the net force for an \emph{underwater:
bubble} contact is denoted by plus symbols. Insets represent the \emph{underwater:
bubble }contact for each substrate.}
\end{figure}
